Ornaments as indicators of social change before and after European arrival at Kiwulan, Northeastern Taiwan

### 2019-08-27 analysis/paper/paper.Rmd

The results show that there is one major core area during the pre-European period, multiple core areas during European period, and a single core during the Chinese period according to the kernal density maps (Figure \@ref(fig:plot-all-densities)). It seems that there are three consistent sub-regions with a core area that shifts over time. The distribution might indicate different household-based social groups who possessed more ornaments. The multiple groups during European period might reflect more unequal consumption of ornaments across the site, relative to other periods, to indicate social processes caused by human behavior. However, it could also just a random pattern resulted from bigger sample size. In addition, the generation of core areas might be biased due to small sample size, for example, a few ornaments found at one single square during the Chinese period could create an obvious hot spot. To further evaluate the pattern, we test the hypothesis that the distribution of ornaments is not randomly distributed to determine if social processes might explain ornament distributions.

>>>>

The results show that there is one major core area during the pre-European period, multiple core areas during European period, and a single core during the Chinese period according to the kernal density maps (Figure \@ref(fig:plot-all-densities)). It seems that there are three consistent sub-regions with a core area that shifts over time. The distribution might indicate different household-based social groups who possessed more ornaments. The multiple groups during European period might reflect more unequal consumption of ornaments across the site, relative to other periods, to indicate social processes caused by human behavior. However, it could also just a random pattern resulting from bigger sample size. In addition, the generation of core areas might be biased due to small sample sizes, for example, a few ornaments found at one single square during the Chinese period could create an obvious hot spot. To further evaluate these patterns, we test the hypothesis that the distribution of ornaments is not randomly distributed to determine if social processes might explain ornament distributions.
